---
title: IEEE template for starwars analysis
date: "`r format(Sys.time(),'%d %B %Y')`"
affiliation:
  ## use one only of the following
  # author-columnar: true         ## one column per author
  institution-columnar: true  ## one column per institution (multiple autors eventually)
  # wide: true                  ## one column wide author/affiliation fields

  institution:
    - name: University of Washington
      department: School of Informatics and Data Science
      location: Seattle, Washington
      email: ece@uw.edu
      mark: 1
      author:
        - name: Advika Battini
    - name: Twentieth Century Fox
      location: Seattle, USA
      mark: 2
      author:
        - name: Homer Simpson
          email: homer@thesimpsons.com
    - name: Starfleet Academy
      location: San Francisco, California 96678-2391
      other: "Telephone: (800) 555--1212, Fax: (888) 555--1212"
      mark: 3
      author:
        - name: Montgomery Scott
    
keywords: ["keyword 1", "keyword 2"]
abstract: |
  Week 4 in class activity

bibliography: mybibfile.bib
output: rticles::ieee_article

---

Introduction
=============
<!-- no \IEEEPARstart -->
This demo file is intended to serve as a ``starter file''
for IEEE conference papers produced under \LaTeX\ using
IEEEtran.cls version 1.8b and later.
<!-- You must have at least 2 lines in the paragraph with the drop letter -->
<!-- (should never be an issue) -->
I wish you the best of success.


## Importing libraries first...

```{r, ,warning=FALSE,message=FALSE}
library(tidyverse)
```

```{r, setup, echo=FALSE}
knitr::opts_chunk$set(
  collapse=TRUE,
  warning = FALSE,
  echo = FALSE,
  comment ="#>")
  
knitr::read_chunk("my_script.R")

```
### In this activity, the following will be done:
1. Uses starwars dataset & tidyverse. \newline
2. Has a plot and table (no need for captions and cross-reference because this is hard with some templates) \newline
3. Has two in-text citations using bibtex  \newline
4. Has a user-friendly, polished structure5.Has a set-up chunk, with 3+ settings  \newline
6. Uses code from an external R script file and knitr::read_chunk()  \newline
7. Uses a template from the rticles/papaja/tufte pkg or similar tufte::tufte_html 
  is a good option if you get LaTeX errors with other templates. 
  You can delete the code and text in the template, but don’t remove any YAML.  \newline
8. Uses knitr caching on at least one chunk
  Setup chunk with 3+ settings and reading external code  \newline
  
Plotting
============
### Using external R code and plotting a figure


```{r set-print-data,echo=FALSE}
<<set-print-data>>
```

```{r starwarsplot, fig.cap="A ggplot of starwars stuff"}
starwars %>%
  filter(species=="Human") %>%
  ggplot() +
  aes(x=height,y=mass)+
  geom_point()
```

### Using caching

```{r}

  if (file.exists('my_cache.rds')){
    ref <- readRDS('my_cache.rds')
    
  }else{
    ref <- c(1,2,3,4)
    saveRDS(ref,'my_cache.rds')
  }

  print(ref)
```

Benefits of Parametrization
============
Parameterized reports extend the reproducibility of R Markdown by allowing us to specify one or more parameters to customize the analysis. This is useful if we want to create a report template that can be reused across multiple similar scenarios. Examples may include:
• Showing results for a specific geographic location. \newline
• Running a report that covers a specific time period. \newline
• Running a single analysis multiple times for different assumptions. \newline
• Controlling the behavior of knitr (e.g., specify if you want the code to be displayed in one version of the output and not displayed in another). \newline

<!-- An example of a floating figure using the graphicx package. -->
<!-- Note that \label must occur AFTER (or within) \caption. -->
<!-- For figures, \caption should occur after the \includegraphics. -->
<!-- Note that IEEEtran v1.7 and later has special internal code that -->
<!-- is designed to preserve the operation of \label within \caption -->
<!-- even when the captionsoff option is in effect. However, because -->
<!-- of issues like this, it may be the safest practice to put all your -->
<!-- \label just after \caption rather than within \caption{}. -->

<!-- Reminder: the "draftcls" or "draftclsnofoot", not "draft", class -->
<!-- option should be used if it is desired that the figures are to be -->
<!-- displayed while in draft mode. -->

<!-- \begin{figure}[!t] -->
<!-- \centering -->
<!-- \includegraphics[width=2.5in]{myfigure} -->
<!-- where an .eps filename suffix will be assumed under latex,  -->
<!-- and a .pdf suffix will be assumed for pdflatex; or what has been declared -->
<!-- via \DeclareGraphicsExtensions. -->
<!-- \caption{Simulation results for the network.} -->
<!-- \label{fig_sim} -->
<!-- \end{figure} -->

<!-- Note that the IEEE typically puts floats only at the top, even when this -->
<!-- results in a large percentage of a column being occupied by floats. -->


<!-- An example of a double column floating figure using two subfigures. -->
<!-- (The subfig.sty package must be loaded for this to work.) -->
<!-- The subfigure \label commands are set within each subfloat command, -->
<!-- and the \label for the overall figure must come after \caption. -->
<!-- \hfil is used as a separator to get equal spacing. -->
<!-- Watch out that the combined width of all the subfigures on a  -->
<!-- line do not exceed the text width or a line break will occur. -->

<!-- \begin{figure*}[!t] -->
<!-- \centering -->
<!-- \subfloat[Case I]{\includegraphics[width=2.5in]{box}% -->
<!-- \label{fig_first_case}} -->
<!-- \hfil -->
<!-- \subfloat[Case II]{\includegraphics[width=2.5in]{box}% -->
<!-- \label{fig_second_case}} -->
<!-- \caption{Simulation results for the network.} -->
<!-- \label{fig_sim} -->
<!-- \end{figure*} -->

<!-- Note that often IEEE papers with subfigures do not employ subfigure -->
<!-- captions (using the optional argument to \subfloat[]), but instead will -->
<!-- reference/describe all of them (a), (b), etc., within the main caption. -->
<!-- Be aware that for subfig.sty to generate the (a), (b), etc., subfigure -->
<!-- labels, the optional argument to \subfloat must be present. If a -->
<!-- subcaption is not desired, just leave its contents blank, -->
<!-- e.g., \subfloat[]. -->


<!-- An example of a floating table. Note that, for IEEE style tables, the -->
<!-- \caption command should come BEFORE the table and, given that table -->
<!-- captions serve much like titles, are usually capitalized except for words -->
<!-- such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to -->
<!-- and up, which are usually not capitalized unless they are the first or -->
<!-- last word of the caption. Table text will default to \footnotesize as -->
<!-- the IEEE normally uses this smaller font for tables. -->
<!-- The \label must come after \caption as always. -->

<!-- \begin{table}[!t] -->
<!-- % increase table row spacing, adjust to taste -->
<!-- \renewcommand{\arraystretch}{1.3} -->
<!-- if using array.sty, it might be a good idea to tweak the value of -->
<!-- \extrarowheight as needed to properly center the text within the cells -->
<!-- \caption{An Example of a Table} -->
<!-- \label{table_example} -->
<!-- \centering -->
<!-- % Some packages, such as MDW tools, offer better commands for making tables -->
<!-- % than the plain LaTeX2e tabular which is used here. -->
<!-- \begin{tabular}{|c||c|} -->
<!-- \hline -->
<!-- One & Two\\ -->
<!-- \hline -->
<!-- Three & Four\\ -->
<!-- \hline -->
<!-- \end{tabular} -->
<!-- \end{table} -->


<!-- Note that the IEEE does not put floats in the very first column -->
<!-- - or typically anywhere on the first page for that matter. Also, -->
<!-- in-text middle ("here") positioning is typically not used, but it -->
<!-- is allowed and encouraged for Computer Society conferences (but -->
<!-- not Computer Society journals). Most IEEE journals/conferences use -->
<!-- top floats exclusively.  -->
<!-- Note that, LaTeX2e, unlike IEEE journals/conferences, places -->
<!-- footnotes above bottom floats. This can be corrected via the -->
<!-- \fnbelowfloat command of the stfloats package. -->


Conclusion
============

This is the end of the week 4 in class activity.

<!-- conference papers do not normally have an appendix -->

Acknowledgment {#acknowledgment}
==============

The authors would like to thank Rstudio

The summary table is as follows:
\onecolumn
```{r starwarstbl}
starwars %>%
  filter(species=='Human') %>%
  select(name,height,mass) %>%
  knitr::kable(caption="A knitr kable table of starwars data")

```

\twocolumn

Bibliography styles
===================

Here are some sample references: @gareau2011bacterial , @clarkson2017human , @Feynman1963118 , [@Dirac1953888].

\newpage
References {#references .numbered}
==========

